systemfit: A Package for Estimating\\ Systems of Simultaneous Equations in \proglang{R}

### 2007-07-04 paper/trunk/JSS/response_B.tex

\subsection{Number of observations}
% Page 2: 'observations' should be explained earlier together with the presentation of the data
% structure. The number of observations should be stated.

We have included a brief statement that the number of observations for
each equation in the system is the same.

\subsection{x and y variables}
% Page 2: It should be clarified whether y-variables in one equation can be x-variables in another.

This is stated in the introduction (page 2, lines 14-15).

\subsection{Instrumental variables}
% Page 4, line 82: 'may' should be 'must'. Here the difference is extremely important. Maybe the text
% could emphasize more clearly what is required of a variable if it is to be used as an instrumental
% variable. What is a good instrumental variable and what happens if the requirements are not
% fulfilled?

@@

The selection of instrument variables is discussed in more detail in
other references and may quite unique to each field. 
We chose not to focus on details such as selection of instrument
variables, variance-covariance structures and other specifics of
simultaneous equations as this article was written to present the
basic equations, fitting methods and usage of the software package.
While we desired to include a wide variety of topics, such as
structure of the residual variance-covariance matrix, many of these
were included in the package to compare, and finally match, the
results from other software packages.
For guidance on selection of instrument variables, the reader is
referred to the citations in the article.

\subsection{Equation 20 and 23}
% The difference between equation 20 and 23 is so smaller that maybe it should be noted in the text
% what it is.

We have added a note to make the reader aware of the difference
between these two equations.

\subsection{Residual covariance matrix (Sigma)}
% Line 193-194: Language is confusing. It should be explained that calculation of some of the
% estimators earlier introduced require Sigma to be known. Often Sigma is not known so an estimator
% is used instead. However, then statistical properties may changed compared to the theory described
% earlier.

We have described this issue more clearly now.
For instance in sections~2.1 and~2.2, the residual covariance matrix
is no longer treated as known.
Hence, the fact that $\Sigma$ and $\Omega$ are unknown and have to be estimated
is no longer °hidden° in section 2.3.

@@

\subsection{First step OLS}
% Line 196: It should be explained what is meant by a first step OLS.

We have explained the two-step procedure
to obtain the estimated residual covariance matrix
more clearly now.

### 2007-07-04 paper/trunk/systemfit_estimation.tex
improved description of two-step method to obtain FGLS results (suggested by referee B)
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@789 591db2bd-e0a0-4d22-8c19-2192dbb7da31
minor (but important) correction suggested by referee B (may -> must); added answer to referee B that we have done this
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@791 591db2bd-e0a0-4d22-8c19-2192dbb7da31

The Weighted Least Squares (WLS) estimator allows for different variances
of the disturbance terms in the different equations
$( \sigma_i^2 \neq \sigma_j^2 \, \forall \, i \neq j$,
where $\sigma_i^2 = \E [ u_{it}^2 ])$.
The WLS estimator can be obtained by
\begin{equation}
   \bHat_{WLS} = \left( X' \OHat^{-1} X \right)^{-1} X' \OHat^{-1} y ,
\end{equation}
where $\OHat = \SHat \otimes I$,
$\sHat_{ij} = 0 \; \forall \; i \neq j$ and
$\sHat_{ii} = \sHat_i^2$ is the variance
of the (estimated) residuals in the $i$th equation.
Theoretically, it would be better to use the variances of
the (true) disturbances $( \sigma_{ii} )$.
However, they are not known in most empirical applications.
Therefore, true variances are generally replaced by estimated variances
$( \sHat_{ii} )$
that are calculated from the residuals of a first-step OLS estimation
(see section~\ref{sec:residcov}).

@@

If the regressors of one or more equations are correlated 
with the disturbances ($\E \left[ u_i' X_i \right] \neq 0$),
OLS estimates are biased.
This can be circumvented by an instrumental variable (IV)
two-stage least squares (2SLS) estimation.
The instrumental variables for each equation $H_i$ 
can be either different or identical for all equations.
The instrumental variables of each equation may not be correlated with 
the disturbance terms of the corresponding equation 
($\E \left[ u_i' H_i \right] = 0$).

>>>>

The Weighted Least Squares (WLS) estimator allows for different variances
of the disturbance terms in the different equations
$( \sigma_i^2 \neq \sigma_j^2 \, \forall \, i \neq j$,
where $\sigma_i^2 = \E [ u_{it}^2 ])$.
The WLS estimator can be obtained by
\begin{equation}
   \bHat_{WLS} = \left( X' \OHat^{-1} X \right)^{-1} X' \OHat^{-1} y ,
\end{equation}
where $\OHat = \SHat \otimes I$,
$\sHat_{ij} = 0 \; \forall \; i \neq j$ and
$\sHat_{ii} = \sHat_i^2$ is the variance
of the (estimated) residuals in the $i$th equation.
Theoretically, $\sHat_{ii}$ should be the variance of
the (true) disturbances $( \sigma_{ii} )$.
However, they are not known in most empirical applications.
Therefore, true variances are generally replaced by estimated variances
$( \sHat_{ii} )$
that are calculated from the residuals of a first-step OLS estimation
(see section~\ref{sec:residcov}).

@@

If the regressors of one or more equations are correlated 
with the disturbances ($\E \left[ u_i' X_i \right] \neq 0$),
OLS estimates are biased.
This can be circumvented by an instrumental variable (IV)
two-stage least squares (2SLS) estimation.
The instrumental variables for each equation $H_i$ 
can be either different or identical for all equations.
The instrumental variables of each equation must not be correlated with
the disturbance terms of the corresponding equation 
($\E \left[ u_i' H_i \right] = 0$).
